---
title: "ESDA Machine Learning Bootcamp"
author: "Georg Maubach"
date: "16 August 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

Day 1: 16.08.2017

# Regression  

## Ordinary Least Squares (OLS)  

```{r}
library(car)

# Careers in the United States
data("Duncan")
head(Duncan)
sapply(Duncan, unique)

```

Models are build using the following notation:  

- model name
- target variable(s)
- tilde
- input variable(s)
- dataset where to find input and target variable(s)

model <- lm(temperature ~ . , dataset) means that all variables are taken
without the target variable "temperature".

```{r}
model = lm(prestige ~ education, Duncan)
plot(prestige ~ education, Duncan)

f <- function(x) {
  predict(
    model,
    data.frame(education = x)
  )
}

plot(f, from = 0, to = 100, add = TRUE)

new_data <- data.frame(education = c(10, 50, 90))
# colums must match up with the columns in the model
new_data
predict(model, new_data)

```

## Generalized Linear Models (GLM)  

```{r}
data("airquality")
head(airquality)

plot(Ozone~Wind, airquality)
model_1 <- lm(Ozone ~ Wind, airquality)
f_1 <- function(x) {
  predict(
    model_1,
    data.frame(Wind = x)
  )
}

# plot function f_1 gets its parameter x from the expression 
# "from = 0, to = 25"
plot(f_1, from = 0, to = 25, add = TRUE)

model_2 <- glm(Ozone ~ Wind, "poisson", airquality)
f_2 <- function(x) {
  predict(
    model_2,
    data.frame(Wind = x),
    type = "response"
  )
}

plot(f_2, from = 0, to = 25, add = TRUE, col = "red")
```

## Polynomial Regression  

```{r}
poly(1:4, raw = TRUE, simple = TRUE)
model_3 <- lm(Ozone ~ poly(Wind, 4), airquality)
f_3 <- function(x) {
  predict(
    model_3,
    data.frame(Wind = x)
  )
}

plot(f_3, from = 0, to = 25, add = TRUE)
```

## Neural Networks

```{r}
# Package "nnet"
# - package can handle only one hidden layer
# - uses only the logistic (sigmoid) function

# install.packages("nnet", dependencies = TRUE)

library(nnet) 
model_4 <- nnet(Ozone ~ Wind, airquality, size = 4, linout = TRUE)

f4 <- function(x) {
  predict(
    model_4,
    data.frame(Wind = x)
  )
}

plot(f4, from = 0, to = 25, add = TRUE, col = "orange")
 ```

## Excercise 1

Use datasets.R

2017-08-16_Excercise_1.R

Use ex1.R for soluton

## Excercise 2: Regression

Use datasets.R

2017-08-16_Excercise_2.R

Use regression.R for soluiton

# Validation  

**Please note**  
Make always sure that you randomize the complete dataset before splitting it
into training, evaluation and test data cause you can never be sure that the
data was collected or delivered randomly. Normally the data collectors sort the
data to make checks.  

## Excercise 3: Model Validation / Selection Excercises

Use datasets.R
Use selection.R for solution

# Regularisation

Use regularisation.R

# How To Split Your Data?  

Answer the 3 questions from the slides.

Use Learning Graphs in your work to split data.





